The Strong Gravitational Lens Finding Challenge

### 2017-09-08 paper.tex
Update on Overleaf.

\subsection{Convolutional Neural Networks ((Lanusse)}
Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later a brief general description of them will be useful.
A CNN \citep{Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images. With the very recent advances of the \textit{Deep Learning} framework \citep{Lecun2015}, models based on CNN architectures have reached or even surpassed human accuracy in image classification tasks \citep{He2015a}.

>>>>

\subsection{Convolutional Neural Networks}
Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later a brief general description of them will be useful.
A CNN \citep{Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images. With the very recent advances of the \textit{Deep Learning} framework \citep{Lecun2015}, models based on CNN architectures have reached or even surpassed human accuracy in image classification tasks \citep{He2015a}.
